Carrier phase and amplitude estimation of $M$-ary phase shift keying using pilots and data

### 2012-05-12 paper.tex
Added to paper.

\begin{lemma}\label{lem:Qconv}
\[
\sqrt{L} Q(\hat{\lambda}_L) = \sqrt{L} \hat{\lambda}_L\big( ph_1(0) + ?  + o_P(1) \big)
\]
\end{lemma}
\begin{IEEEproof}
Write
\[
Q(\lambda) = \prob G_L^\prime(\lambda) - \prob G_L^\prime(0) = \frac{\abs{P}}{L} k_1(\lambda) + \frac{\abs{D}}{L} k_2(\lambda)
\]
where
\begin{align*}
k_1(\lambda) &= \prob R_1\big( \sin(\lambda + \Phi_1) - \sin(\Phi_1) \big), \;\;\; \text{and} \\
k_2(\lambda) &= \prob R_1\big( \sin\fracpart{\lambda + \Phi_1} - \sin\fracpart{\Phi_1} \big).
\end{align*}
Since
\[
\sin(\lambda + \phi) - \sin(\phi) = \lambda \big( \cos(\phi) + \zeta(\lambda) \big)
\]
where $\zeta(\lambda)$ is a function that goes to zero as $\lambda$ goes to zero, then
\begin{align*}
k_1(\lambda) &= \prob R_1\lambda(\cos(\Phi_1) \; + \; \zeta(\lambda)) \\
&= \lambda \big( \prob R_1\cos(\Phi_1) \; + \; \zeta(\lambda) \prob R_1 \big) \\
&= \lambda \big( h_1(0) \; + \; \zeta(\lambda) K \big),
\end{align*}
where we put $K = \prob R_1$, a finite constant.  Because $\hat{\lambda}_L$ converges almost surely to zero as $L \rightarrow\infty$, then $\zeta(\hat{\lambda}_L)$ converges almost surely (and therefore also in probability) to zero as $L \rightarrow\infty$, i.e. $\zeta(\hat{\lambda}_L) = o_P(1)$.  So, 
\begin{align*}
k_1(\hat{\lambda}_L) &= \hat{\lambda}_L \big( h_1(0) \; + \; \zeta(\hat{\lambda}_L) K \big) \\
&= \hat{\lambda}_L \big( h_1(0)  + o_P(1)\big).
\end{align*}
\end{IEEEproof}

\begin{lemma}\label{lem:empiricprocc} BLERG
\[
\sqrt{L}\big( G_L^\prime(\hat{\lambda}_L) - Q(\hat{\lambda}_L) \big) = o_P(1) + \sqrt{L} G_L^\prime(0).
\]
\end{lemma}
\begin{IEEEproof}
\end{IEEEproof}

@@

\begin{lemma}\label{lem:XL} 
The distribution of $X_L$ converges to the normal with zero mean and covariance
\[
?
\]
as $L \rightarrow\infty$.
\end{lemma}
\begin{IEEEproof}
\end{IEEEproof}

\begin{lemma}\label{lem:XLcovlambdaL} 
The covariance between $X_L$ and $\sqrt{L}\hat{\lambda}_L$ converges to zero as $L\rightarrow\infty$.
\end{lemma}
\begin{IEEEproof}
\end{IEEEproof}

>>>>

\begin{lemma}\label{lem:Qconv}
\[
\sqrt{L} Q(\hat{\lambda}_L) = \sqrt{L} \hat{\lambda}_L\big( p + ?  + o_P(1) \big)
\]
\end{lemma}
\begin{IEEEproof}
Write
\[
Q(\lambda) = \prob G_L^\prime(\lambda) - \prob G_L^\prime(0) = \frac{\abs{P}}{L} k_1(\lambda) + \frac{\abs{D}}{L} k_2(\lambda)
\]
where
\begin{align*}
k_1(\lambda) &= \prob R_1\big( \sin(\lambda + \Phi_1) - \sin(\Phi_1) \big), \;\;\; \text{and} \\
k_2(\lambda) &= \prob R_1\big( \sin\fracpart{\lambda + \Phi_1} - \sin\fracpart{\Phi_1} \big).
\end{align*}
Since,
\[
\sin(\lambda + \phi) - \sin(\phi) = \lambda \big( \cos(\phi) + \zeta(\lambda) \big),
\]
where $\zeta(\lambda)$ is a function that goes to zero as $\lambda$ goes to zero, then
\begin{align*}
k_1(\lambda) &= \prob R_1\lambda(\cos(\Phi_1) \; + \; \zeta(\lambda)) \\
&= \lambda \big( \prob R_1\cos(\Phi_1) \; + \; \zeta(\lambda) \prob R_1 \big) \\
&= \lambda \big( 1 \; + \; \zeta(\lambda) K \big),
\end{align*}
since $h_1(0) = \prob R_1\cos(\Phi_1) = 1$ and where we put $K = \prob R_1$, a finite constant.  Because $\hat{\lambda}_L$ converges almost surely to zero as $L \rightarrow\infty$, then $\zeta(\hat{\lambda}_L)$ converges almost surely (and therefore also in probability) to zero as $L \rightarrow\infty$, i.e. $\zeta(\hat{\lambda}_L) = o_P(1)$.  So, 
\[
k_1(\hat{\lambda}_L) = \hat{\lambda}_L \big( 1 \; + \; \zeta(\hat{\lambda}_L) K \big) = \hat{\lambda}_L \big( 1  + o_P(1)\big).
\]
Recalling that $f(r,\phi)$ is the joint probability density function of $R_1$ and $\Phi_1$,
\begin{align*}
k_2(\lambda) &= \int_0^{2\pi}\int_{0}^\infty r \big( \sin\fracpart{\lambda + \phi} - \sin\fracpart{\phi} \big) f(r,\phi) dr d\phi \\
&= \int_0^{2\pi} \big( \sin\fracpart{\lambda + \phi} - \sin\fracpart{\phi} \big) g(\phi) d\phi.
\end{align*}
Now, if $0 \leq \lambda < \tfrac{\pi}{M}$, then for each integer $k$,
\begin{align*}
\sin\fracpart{\lambda + \phi} - \sin\fracpart{\phi} &= \sin(\lambda + \phi - \tfrac{2\pi k}{M}) - \sin(\phi - \tfrac{2\pi k}{M}) \\
&= \lambda\big(\cos(\phi - \tfrac{2\pi k}{M}) + \zeta_k(\lambda)\big)
\end{align*}
when $\phi \in [\tfrac{ (2k-1)\pi}{M}, \tfrac{2k\pi}{M} - \lambda )$ and 
\begin{align*}
\sin&\fracpart{\lambda + \phi} - \sin\fracpart{\phi} \\
&= \sin(\lambda + \phi - \tfrac{2\pi k}{M}) - \sin(\phi - \tfrac{2\pi (k-1)}{M}) \\
&=  v_k(\phi) + \lambda\big(\cos(\phi - \tfrac{2\pi k}{M}) + \zeta_k(\lambda)\big) 
\end{align*}
when $\phi \in [ \tfrac{2k\pi}{M} - \lambda,\tfrac{2k\pi}{M} )$, and where
\[
v_k(\phi) = \sin(\phi - \tfrac{2\pi k}{M}) - \sin(\phi - \tfrac{2\pi (k-1)}{M}).
\]
\end{IEEEproof}

\begin{lemma}\label{lem:empiricprocc} BLERG
\[
\sqrt{L}\big( G_L^\prime(\hat{\lambda}_L) - Q(\hat{\lambda}_L) \big) = o_P(1) + \sqrt{L} G_L^\prime(0).
\]
\end{lemma}
\begin{IEEEproof}

\end{IEEEproof}

@@

\begin{lemma}\label{lem:XL} 
The distribution of $X_L$ converges to the normal with zero mean and covariance
\[
?
\]
as $L \rightarrow\infty$.
\end{lemma}
\begin{IEEEproof}

\end{IEEEproof}

\begin{lemma}\label{lem:XLcovlambdaL} 
The covariance between $X_L$ and $\sqrt{L}\hat{\lambda}_L$ converges to zero as $L\rightarrow\infty$.
\end{lemma}
\begin{IEEEproof}

\end{IEEEproof}
